---
title: "grip_data_acq"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(mice)
```

Acquisition and formatting
===

```{r}
grip = read.csv('gripe_propensity.csv')
```

We start removing useless variables (ID):

```{r}
grip$ID <- NULL
```

We start by checking how much missing data there is in every variable:

```{r}
mis =c()
for (i in 1:ncol(grip)){
  print(colnames(grip)[i])
  mis[i]=sum(is.na(grip[,i])==TRUE)
  print(mis[i])
}
```

We see that we have a considerable amount of missing data in some of the variables. Missing data treatment is a delicate issue and in this case can affect our results. 

First we will remove all variables that have 50% or more of missing data, given that they can be of no use to us: 

```{r}
treure = which(mis > (nrow(grip)/2))
cg = grip[,-treure]
```

So we are now left with 67 variables. 

Let's check the percentage of missing data in each variable:

```{r}
permis =c()
for (i in 1:ncol(cg)){
  print(colnames(cg)[i])
  permis[i]=sum(is.na(cg[,i])==TRUE)/nrow(cg)
  print(round(permis[i],2)*100)
}
```

We impute the rest of missings:

```{r}

# aquest és el tros que fa imputació de variables, com que tarda molt ja agafem directament el csv imputat

tcg=mice(cg, method = 'rf')
ttcg=complete(tcg)
 
write.csv(ttcg, 'grip_net.csv')

```

